What is the Effect of X on Y?

### 2023-10-26 latex-slides/slides.tex
Use real figure for slides

\begin{frame}{Components}{Two Columns with Figure}
  \begin{columns}[T]
    \begin{column}{.54\textwidth}
      \includegraphics[width=\textwidth]{img/kanagawa.jpg}
    \end{column}
    \hfill
    \begin{column}{.46\textwidth}
      \begin{itemize}
      \item A point about the figure that is potentially important.
      \item Another point about the figure that is also potentially important.
      \end{itemize}
    \end{column}
  \end{columns}
\end{frame}

@@

% 4:3 ratio for figures
% or else it will have white space
\imageframe{img/kanagawa_16_9.png}

@@

\begin{frame}{Figure}{}
  The \texttt{adjustbox} environment helps resize figures/tables

  \medskip
  \begin{adjustbox}{width = 0.7\textwidth, center}
    \includegraphics{img/kanagawa_16_9.png}
  \end{adjustbox}
\end{frame}

>>>>

\begin{frame}{Components}{Two Columns with Figure}
  \begin{columns}[T]
    \begin{column}{.54\textwidth}
      \includegraphics[width=\textwidth]{figures/plot_did2s_retail_slides.pdf}
    \end{column}
    \hfill
    \begin{column}{.46\textwidth}
      \begin{itemize}
      \item A point about the figure that is potentially important.
      \item Another point about the figure that is also potentially important.
      \end{itemize}
    \end{column}
  \end{columns}
\end{frame}

@@

% 4:3 ratio for figures
% or else it will have white space
\imageframe{figures/plot_did2s_retail_slides.pdf}

@@

\begin{frame}{Figure}
  \begin{adjustbox}{width = 0.75\textwidth, center}
    \includegraphics{figures/plot_did2s_retail_slides.pdf}
  \end{adjustbox}
  \note{The \texttt{adjustbox} environment helps resize figures/tables}
\end{frame}
